NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-27 paper/pipeline.tex
update eaquation
update pipeline

\subsection{Pipeline View}

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipelineView}
 \caption{
Visual representation of the three stages (encoder, attention, classifier) model. In the proposed tool, we allow the model parameter to be updated to fix a prediction error. The pipeline view, by showing the aggregated gradient distribution, inform the user about the how different part of the model response to the optimization.
%
The optimization parameters is shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ). In (c), we select whether if we want to use current update setting as display or try all the configuration combination (i.e., update for each stage can be enabled or disabled).
 }
\label{fig:modelPipeline}
\end{figure}

\subsubsection{Margin-Infused Relaxed Algorithm (MIRA)}
the mira loss is $|w' - w|^2 + C * J(w')$

>>>>

\subsection{Pipeline View}
\label{sec:pipeline}
Pipeline view provides a direct visual representation of the three stages (encoder, attention, classifier) of the model. In the proposed tool, we allow the model parameter to be updated (via an optimization) to correct a prediction error (\textbf{T3}). The pipeline view, by visualizing the aggregated gradient distribution, informs the user on the how each stage of the model responses to the optimization.

There are many ways to update the model to correct a prediction. The simplest way to achieve it is applying standard backpropagation that overfits to the example. However, without any constraint, the update step may alter the model in unexpected ways.
% \shusen{what is the benefit of using mira?}
Instead, we adopted the \emph{Margin-infused relaxed algorithm (MIRA)}~\cite{CrammerSinger2003} update, where we regulate the optimization with the amount of change to the parameter. In the proposed tool, we define the MIRA loss as the following:
\begin{equation}
\underset{w'}{\mathrm{argmin}}( C_{mira} \mathbb{J}(\mathbf{W}') + ||\mathbf{W}' - \mathbf{W}||),
\end{equation}
where $\mathbb{J}(\mathbf{W})$ is the lost function for the model, and $\mathbf{W}$ is the original model's parameters, and $\mathbf{W}'$ is the updated parameters. $C_{mira}$ is the weighting term, which determines whether we intended to emphasis more on obtaining better fitting or deviating less from the original model.
%
Under this formation, we try to find the best approximation to the newly assigned label, while still maintaining relatively small change with respect to the original model.

As illustrated in Fig.~\ref{fig:pipelineView},
the optimization hyperparameters are shown in Fig.~\ref{fig:pipelineView}(a). Each of the stages is illustrated by a glyph (Fig.~\ref{fig:pipelineView}(b)), in which the user can enable or disable its parameter update by click on the parameter bar (the legend about its state is shown in Fig.~\ref{fig:pipelineView}(d) ). In Fig.~\ref{fig:pipelineView}(c), we select whether if we want to use current update setting as displayed or try all the configuration combination (i.e., each stage can either be enabled or disabled for the three stage, therefore, there are $8$ combinations in total, $7$ if discard the case where all stages are not updated).

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipelineView}
 \caption{
 The pipeline view provides the visual representation of three stages (encoder, attention, classifier) model. In the proposed tool, we allow the model parameter to be updated to correct a prediction error. The pipeline view, by showing the aggregated gradient distribution, informs the user about the how different part of the model response to the optimization.
 %
 The optimization hyperparameters are shown in (a), each of the stages is illustrated in (b), where the user can click on the parameter bar to enable or disable its update (the legend about its state is shown in (d) ). In (c), we select whether if we want to use current update setting as displayed or try all the possible configuration combination (i.e., each stage's parameter update can be enabled or disabled).
 }
\label{fig:pipelineView}
\end{figure}

% \textbf{Margin-Infused Relaxed Algorithm (MIRA)}
